% metadata, imports, contact information, etc.
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Brandon Gutierrez}
\address{\href{tel:+15125545818}{\underline{+1(512)-554-5818}} \\ \href{mailto:bran09123@gmail.com}{\underline{bran09123@gmail.com}}} 
\address{\href{https://github.com/gutibran}{\underline{github.com/gutibran}} \\ \href{https://linkedin.com/in/gutibran}{\underline{linkedin.com/in/gutibran}} \\ \href{https://gutibran.com}{\underline{gutibran.com}}}

\begin{document}
    %----------------------------------------------------------------------------------------
    %	OBJECTIVE
    %----------------------------------------------------------------------------------------
    %\begin{rSection}{OBJECTIVE}
    %    {Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}
    %\end{rSection}

    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Education}
        {\bf Bachelor of Science in Electrical Engineering}, Texas State University \hfill {Expected 2028} \\
        % Relevant Coursework: A, B, C, and D.
        Minor in Applied Mathematics \smallskip
        %{\bf Bachelor of Computer Science}, Stanford University \hfill {2014 - 2017}
        %Member of Eta Kappa Nu \\
        %Member of Upsilon Pi Epsilon \\
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	CERTIFICATIONS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Certifications}
        {\bf CompTIA Security+} \hfill {Expected October 2024}
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	PERSONAL PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Personal Projects} \vspace{-1.25em}
        \item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
        \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
        \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
    \end{rSection} 

    %----------------------------------------------------------------------------------------
    %   WORK EXPERIENCE SECTION 
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Work Experience}
        \textbf{Cold Food Production Associate} \hfill May 2024 - August 2024 \\
        LSG Sky Chefs \hfill \textit{Austin, TX}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Assembled and packaged food trays according to airline specifications and safety standards.
            \item Worked with a team to meet daily production quotas and deadlines under time-sensitive conditions.
        \end{itemize}
        
        \textbf{Lot Loader} \hfill November 2022 - October 2023 \\
        The Home Depot \hfill \textit{Austin, TX}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Provided support with heavy lifting, ensuring safe transport of large or bulky items to customers' vehicles.
            \item Ensured that walkways and parking areas were free of obstacles to maintain a safe environment for shoppers.
        \end{itemize}

        \textbf{Perishables Representative} \hfill October 2020 - February 2022 \\
        The Home Depot \hfill \textit{Austin, TX}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Replenished fruits and vegetables on the sales floor, ensuring items were well-displayed and fully stocked.
            \item Inspected produce regularly, removing any damaged or expired items to maintain freshness and quality for customers.
            \item Assisted in organizing and categorizing inventory to ensure proper stock levels and reduce waste.
        \end{itemize}
    \end{rSection} 

    %----------------------------------------------------------------------------------------
    %   SKILLS SECTION 
    %----------------------------------------------------------------------------------------
    \begin{rSection}{SKILLS}
        Linux server administration, Scripting, Bash, Python, Linux, MySQL, C++, C, Git
        %\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            %XYZ & A, B, C, D \\
        %\end{tabular}
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %   EXTRA CURRICULAR SECTION 
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Extra-Curricular Activities} 
        \begin{itemize}
            \item Actively write \href{https://gutibran.com/blog}{blog posts} and create \href{https://youtube.com/@gutibran}{technical videos} about various topics that I am learning about. Primarily network security, software engineering, mathematics, artificial intelligence, and robotics.
        \end{itemize}
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %   LEADERSHIP SECTION 
    %----------------------------------------------------------------------------------------
%    \begin{rSection}{Leadership} 
%        \begin{itemize}
%            \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
%        \end{itemize}
%    \end{rSection}
\end{document}