\documentclass{résumé} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Brandon Anthony Gutierrez} % Name
\address{\href{tel:+15125545818}{+1(512)-554-5818} \\ \href{mailto:bran09123@gmail.com}{bran09123@gmail.com}} % PRIMARY CONTACT INFORMATION
\address{\href{https://github.com/gutibran}{github.com/gutibran} \\ \href{https://linkedin.com/in/gutibran}{linkedin.com/in/gutibran} \\ \href{https://gutibran.com}{gutibran.com}}
\begin{document}
%----------------------------------------------------------------------------------------
%    OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{OBJECTIVE}
%{Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}
%\end{rSection}

%----------------------------------------------------------------------------------------
%    EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Bachelor of Electrical Engineering}, Texas State University \hfill {2024 - Current}\\
%Relevant Coursework: A, B, C, and D.
Minor in Applied Mathematics \\
Minor in Computer Science
\end{rSection}
%----------------------------------------------------------------------------------------
%    CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{CERTIFICATIONS}
{\bf CompTIA Network+} \hfill {Feb 2024} \\
{\bf CompTIA Security+} \hfill {Feb 2024}
\end{rSection}

%----------------------------------------------------------------------------------------
%    TECHINICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    General Skills & Linux system administration, automation, scripting, static site development, web scraping \\
    Programming Language & Python, JavaScript, Bash, PowerShell, C, C++, HTML, CSS, LaTeX \\
    Web servers & NGINX \\
    Web Frameworks & Hugo \\
    Databases & MySQL, PostGreSQL, MongoDB, Redis \\
    Operating Systems & Linux (Debian, Arch), Windows (10, 11), MacOS \\
    Software & Microsoft Office (Excel, Word, Powerpoint) \\
    Version Control & Git, GitHub \\
    CI/CD & GitHub Actions \\
    Protocols & SSH, HTTP/HTTPS, SMTP, POP3, IMAP, DNS, DHCP, FTP/SFTP, RDP, VPN, VoIP, \\ & LDAP, VNC, BitTorrent \\
    Miscellaneous & Vim, Docker, LLM prompting, google "dorking", troubleshooting, virtualization, \\ & search engine optimization (SEO), website optimization, computer hardware
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%    PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{\href{https://gutibran.com/bittorrent-client}{BitTorrent Client}} \\
- Developed a custom BitTorrent client in Python.
\item \textbf{\href{https://twitter.com/secplusdailybot}{Twitter Bot}} \\
- Implemented a Twitter (X) bot in Python.
\end{rSection} 

%----------------------------------------------------------------------------------------
%    WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}
\textbf{Sales \& Lot Associate} \hfill October 2022 - Current \\ The Home Depot, \textit{Austin, TX} \\
- Collaborated with the customer service department to handle escalated concerns and maintain customer satisfaction. \\
- Mentored new cashier and lot associates on company policies, job duties, cash handling procedures, and customer interaction. \\ 
\textbf{Front Desk \& Janitorial Engineer} \hfill May 2022 - September 2022 \\ HT Fitness, \textit{Austin, TX} \\
- Managed basic administrative tasks for clients, including appointment scheduling, document filing, and phone inquiries. \\ 
- Conducted janitorial maintenance, ensuring cleanliness and hygiene throughout the premises. \\
\textbf{Perishables Representative} \hfill October 2020 - February 2022 \\ HEB, \textit{Austin, TX} \\
- Efficiently stocked shelves in the produce department, ensuring a well-organized and visually appealing display. \\
- Facilitated the processing of daily inventory, including accurate counting and recording produce stock levels. \\
- Regularly inspected and culled old or damaged products, maintaining high standards of freshness and quality. \\
\textbf{Merchandising Associate} \hfill September 2019 - October 2020 \\ Target, \textit{Austin, TX} \\
- Efficiently stocked shelves in the Toy department, ensuring a visually appealing and well-organized product presentation. \\
- Collaborated with team members to manage inventory levels, optimize product availability, and boost sales. \\
\textbf{Cashier} \hfill November 2016 - August 2019 \\ HEB, \textit{Austin, TX} \\
- Provided excellent customer service by addressing inquiries, resolving issues, and facilitating positive interactions at the point of sale. \\
- Proficiently processed various forms of payment, encompassing cash, credit cards, and debit cards, among others, with a strong focus on accuracy and efficiency.
\end{rSection} 

%----------------------------------------------------------------------------------------
%    MISCELLANEOUS
%----------------------------------------------------------------------------------------
%\begin{rSection}{Extra-Curricular Activities} 
%\begin{itemize}
%    \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
%    \item	Sample bullet point.
%\end{itemize}
%\end{rSection}
\end{document}
